R Notebook

### 2017-02-14 manuscript/draft.Rmd
Draft of Introduction

Quality of predictions is important:
  * helps determine policy/set priorities
  * something something climate change
  * need to know both accuracy of point estimates and how reasonable our prediction intervals are.
  * Overconfident predictions can be worse than uncertainty
  * Quality of prediction is one metric for how much we know about ecological processes
Unclear how much to trust existing predictions:
  * Strong assumptions (see "misc" below)
  * many *interesting* predictions
  * Potential problems with confidence intervals
  * Potential disconnect between training target and actual goals
  * Difficult to test model assumptions/predictions because of time scales
    * Most scientists making predictions today will have retired by 2050
Demonstrate best practices \& their contribution to better predictions
  * Use long-term data sets such as BBS to evaluate predictive skill
  * Note the large change in average temperatures since the 80's; comparable to 
    the potential changed in the next 20 years 
  * Lots of talk about how we should do it, fewer examples of doing them all together
  * Examples of best practices
    * Not just bioclim
    * Dynamic predictor variables (not just site-level averages over 50 years like 
      Worldclim)
    * time series models (temporal autocorrelation)
    * spatial/site-level stuff (repeated measures aren't fully independent)
    * Properly handling uncertainty:
      * probabilistic/error bars
      * error propagation
    * multiple models
      * Test with simple baselines (e.g. random walk, future-is-like-present)
  * Focus on richness/diversity because \[citations saying that it's important\]
  * Publish forecasts at different timescales to evaluate performance/credibility
Here we do that:
  * forecasts for biodiversity in NAmerican birds with as many best practices as 
    possible
  * Discuss the influence of these improved methods \& of our error rates on our 
    ability to understand:
    * How to improve
    * How much to trust the predictions

>>>>

Forecasting the future state of ecological systems is increasingly important for
planning, management, and testing the performance of ecological models
[@clark2001, @dietz2017]. One area of particular interest for forecasting is
biodiversity since it is important for ecosystem function, central to
conservation planning, and expected to be influenced by anthropogenic global
change. Anticipating potential changes in biodiversity is crucial for large
scale management and conservation, and for addressing debates regarding whether
local scale diversity is declining and may continue to decline in response to
anthropogenic influences [@dornelas2014].

Previous efforts to predict future patterns of species richness, and diversity
more generally, have focused primarily on building species distributions models
to quantify the spatial relationships between the occurrence of individual
species and the environment. Forecasts for future environmental conditions are
then used to predict where each species will occur in the future and the
probabilities of occurrence are summed across species to predict future species
richness [e.g., @thomas2004]. Alternatively, models that directly relate spatial
patterns of species richness to the environment have been developed and
generally perform equivalently to species distribution modeling based methods
[@algar2009, @distler2015].

However, despite the emerging interest in forecasting species richness and other
aspects of biodiversity, little is known about how effectively we can anticipate
their dynamics. What we do know comes from a small number of hindcasting
studies, where models are built using data on species occurrence and richness
from the past and evaluated on their ability to predict contemporary patterns
[e.g., @algar2009, @distler2015]. These studies are a valuable first step, but
lack several components that are important for developing good forecasting
models and understanding how accurately these models can predict the
future. These components of good forecasting and evaluation (Box 1) broadly
involve: 1) expanding the use of data to include biological and environmental
time-series [@treddenick2016]; 2) accounting for uncertainty in observations,
processes, model choice, and forecast evaluation [@dietz2017]; and 3) conducting
meaningful evaluations of the forecasts by hindcasting, archiving short-term
forecasts, and comparing forecasts to baselines to determine if the forecasts
are more accurate than assuming the system is basically static [@Perretti2013].

In this paper we attempt to forecast the species richness of breeding birds at
hundreds of locations throughout North America while following the best
practices in Box 1 for ecological forecasting. To do this we combine 30 years of
time-series data on bird distributions with monthly time-series of climate data
and satellite-based remote-sensing. We compare traditional distribution modeling
based approaches to spatial models of species richness, time-series methods, and
simple baselines. All forecasts model uncertainty and observation, are evaluated
across different time lags using hindcasting, and are publicly archived to allow
future assessment. We discuss the implications of these practices for our
understanding of, and confidence in, the resulting forecasts, and how we can
continue to improve on these approaches in the future.
